Solutions for decentralized AI\\

### 2023-06-17 paper.tex
correccio correu sergi v
Paper keeps growing

\author{\IEEEauthorblockN{Sergi Hernández Burbano de Lara}
\IEEEauthorblockA{\textit{Data Science Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
sergi.hernandez01@estudiant.upf.edu}
\and
\IEEEauthorblockN{Sergi Vila Oriol}
\IEEEauthorblockA{\textit{Telecoms Engineering Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
sergi.vila01@estudiant.upf.edu}
\and
\IEEEauthorblockN{Edgar Espinós Murria}
\IEEEauthorblockA{\textit{Telecoms Engineering Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
edgar.espinos01@estudiant.upf.edu}
}
\maketitle

@@

\section{Introduction}
In recent years, AI models have become a relevant technology in our world: from chatbots to image generators, and many other impressive technologies to come.

These technologies are usually developed by companies that take on the role of developing Deep Learning models, gathering the training data, and training the models with their own computing resources. In the future, it will be no surprise to also see governments taking a leading role in the development and use of deep learning technologies.

@@

Consensus protocols of the form of Proof of Work revolve around the idea of miners competing to solve a problem that is hard to solve but easy to verify. Bitcoin's PoW uses the problem of breaking SHA-256 hashes as the problem that miners have to solve in order to be the leaders of a round.

@@

We use the term Deep Learning model to refer to a certain Deep Learning architecture with some parameters $W$ that have been trained with training data or are still to be trained. Model parameters are initialized at random and trained iteratively using some optimization algorithm like stochastic gradient descent.

@@

So training Deep Learning models is a game of finding the optimal parameters thanks to optimization algorithms, and finding the optimal hyperparameters through a process that involves part trial and error and part educated guesses. Moreover, even if there are algorithms that can find local minima like gradient descent, algorithms that find global optimum are unknown yet algorithms that find the global minimum are unknown yet.

@@

\begin{itemize}
\item In Proof-of-Learning (2019) \cite{}, the authors propose a consensus protocol where "Suppliers" publish machine learning tasks that are solved by "Trainers". The solutions provided by "Trainers" are evaluated by "Validators" that choose the winning node and add the next block to the Blockchain. An unaddressed issue in this paper is how to avoid "Trainers" to simultaneously act as "Validators" and rank their own solutions as the best.
\item The authors of Coin.AI (2019) \cite{} propose using the hash of the previous blocks to determine the hyperparameters used by miners to train the models to ensure the immutability of the Blockchain. They also propose a parallel Proof of Storage distributed system to incentivize nodes to store the models after training. The winner is the first miner that achieves a certain quality threshold. So there is no "Validator" ranking the solutions.
\item BlockML (2019) \cite{} also proposes having "Supplier" and "Miner" roles. In this case, miners themselves collectively rank the solutions proposed by other miners.
\item In Proof-of-Deep-Learning (2019) \cite{}, they only allow one problem submitter that should be honest (they call it "model requester"). They split each round in two phases: the first in which miners train the model and commit to it by publishing it on the Blockchain, and a second phase in which they reveal it to other nodes for them to rank them and choose a winner.
\item The Proof of Artificial Intelligence (PAI) (2020) \cite{} network is composed of many entities: problem submitters (called "Clients"), "Miners", "Supervisors", "Evaluators", and "Verifiers".
\item More recent work such as DLBC (2020)\cite{}, Proof of Learning (PoLe) (2020)\cite{}, or CrowdMine (2022)\cite{} propose very similar protocols to the ones explained before.

@@

As the authors of BlockML cleverly point out, using randomly generated deep learning problems is not useful by construction. So we need to introduce a new entity to the game: problem suppliers.

@@

We ask ourselves if this is a necessary requirement to avoid attacks.

@@

But, since nodes and users are anonymous and unauthenticated, a player can be both a node and a user. Thus, the Byzantine player can submit to the pool a hard problem for which he already knows the solution. When the problem gets to be solved by all the nodes, the Byzantine node can provide the most optimal answer to the problem with higher probability than the other nodes because he had prior knowledge of the problem. So nodes can manipulate their probability of being chosen as the leaders.

@@

\bibitem{b3} euronews. (2019, May 14). A.I. is as threatening as climate change and nuclear war, says historian Yuval Noah Harari [Video]. https://www.euronews.com/2019/05/14/a-i-is-as-threatening-as-climate-change-and-nuclear-war-says-philosopher-yuval-noah-harari

@@

\bibitem{b5} Radford, A., Wu, J., Child, R., Luan, D., Amodei, D., \& Sutskever, I. (2019). Language models are unsupervised multitask learners. OpenAI. https://d4mucfpksywv.cloudfront.net/better-language-models/language-models.pdf

\bibitem{b6} Nakamoto, S. (2008) Bitcoin: A Peer-to-Peer Electronic Cash System. https://bitcoin.org/bitcoin.pdf

>>>>

\author{\IEEEauthorblockN{Sergi Hernández Burbano de Lara}
\IEEEauthorblockA{\textit{Data Science Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
sergi.hernandez01@estudiant.upf.edu}
\and
\IEEEauthorblockN{Sergi Vila Oriol}
\IEEEauthorblockA{\textit{Telecoms Engineering Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
sergi.vila02@estudiant.upf.edu}
\and
\IEEEauthorblockN{Edgar Espinós Murria}
\IEEEauthorblockA{\textit{Telecoms Engineering Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
edgar.espinos01@estudiant.upf.edu}
}
\maketitle

@@

    \section{Introduction}
    In recent years, AI models have become a relevant technology: from chatbots to image generators, and many other impressive applications to come.

    These technologies are usually developed by companies that take on the role of developing Deep Learning models, gathering the training data, and training the models with their own computing resources. In the future, it will be no surprise to also see governments taking a leading role in the development and use of Deep Learning technologies.

@@

    Consensus protocols in the form of Proof of Work revolve around the idea of miners competing to solve a problem that is hard to solve but easy to verify. Bitcoin's PoW uses the problem of breaking SHA-256 hashes as the problem that miners have to solve in order to be the leaders of a round.

@@

    We use the term Deep Learning model to refer to a certain Deep Learning architecture with some parameters $W$ that have been trained with training data or are still to be trained. Model parameters are initialized randomly and trained iteratively using some optimization algorithm like stochastic gradient descent.

@@

    So training Deep Learning models is a game of finding the optimal parameters thanks to optimization algorithms, and finding the optimal hyperparameters through a process that involves part trial and error and part educated guesses. Moreover, even if there are algorithms that can find local minima like gradient descent, algorithms that find global optimum are unknown yet.

@@

    \begin{itemize}
    \item In Proof-of-Learning (2019) \cite{b7}, the authors propose a consensus protocol where ``Suppliers" publish machine learning tasks that are solved by ``Trainers". The solutions provided by ``Trainers" are evaluated by ``Validators" that choose the winning node and add the next block to the Blockchain. An unaddressed issue in this paper is how to avoid ``Trainers" to simultaneously act as ``Validators" and rank their own solutions as the best.
    \item The authors of Coin.AI (2019) \cite{b8} propose using the hash of the previous blocks to determine the hyperparameters used by miners to train the models to ensure the immutability of the Blockchain. They also propose a parallel Proof of Storage distributed system to incentivize nodes to store the models after training. The winner is the first miner that achieves a certain quality threshold. So there is no ``Validator" ranking the solutions.
    \item BlockML (2019) \cite{b9} also proposes having ``Supplier" and ``Miner" roles. In this case, miners themselves collectively rank the solutions proposed by other miners, but they do not provide a solution to prevent ``Miners" from stealing each other solutions. They split each round into a training phase and an evaluation phase.
    \item In Proof-of-Deep-Learning (2019) \cite{b10}, they only allow one problem submitter that should be honest (they call it ``model requester"). They also split each round into two phases: the first in which miners train the model and commit to it by publishing it on the Blockchain, and a second phase in which they reveal it to other nodes for them to rank them and choose a winner.
    \item The Proof of Artificial Intelligence (PAI) (2020) \cite{b11} network is composed of many entities: problem submitters (called "Clients"), "Miners" that perform the training, "Supervisors", "Evaluators" that evaluate the trained models, and "Verifiers". In this case, each round is splitted in four: registration, initialization, training and finalization.
    \item More recent work such as DLBC (2020)\cite{b12}, Proof of Learning (PoLe) (2020)\cite{b13}, or CrowdMine (2022)\cite{b14} propose very similar protocols to the ones explained before.

@@

    As the authors of BlockML cleverly point out, using randomly generated Deep Learning problems is not useful by construction. So we need to introduce a new entity to the game: problem suppliers.

@@

    We ask ourselves if this is a necessary requirement to avoid attacks from dishonest suppliers.

@@

    But, since nodes and users are anonymous and unauthenticated, a player can be both a node and a user. Thus, the Byzantine player can submit to the pool a hard problem for which he already knows the solution. When the problem gets to be solved by all the nodes, the Byzantine node can provide the most optimal answer to the problem with higher probability than the other nodes because he had prior knowledge of the problem. So dishonest nodes can manipulate their probability of being chosen as the leaders.

@@

    \bibitem{b3} euronews. (2019, May 14). A.I. is as threatening as climate change and nuclear war, says historian Yuval Noah Harari [Video]. https://www.euronews.com/2019/05/14/a-i-is-as-threatening-as-climate-change-and-nuclear-war-says-philosopher-yuval-noah-harari.

@@

    \bibitem{b5} Radford, A., Wu, J., Child, R., Luan, D., Amodei, D., \& Sutskever, I. (2019). Language models are unsupervised multitask learners. OpenAI. https://d4mucfpksywv.cloudfront.net/better-language-models/language-models.pdf.

    \bibitem{b6} Nakamoto, S. (2008) Bitcoin: A Peer-to-Peer Electronic Cash System. https://bitcoin.org/bitcoin.pdf.

    \bibitem{b7} Bravo-Marquez, F., Reeves, S., \& Ugarte, M. (2019). Proof-of-Learning: A Blockchain Consensus Mechanism Based on Machine Learning Competitions. https://doi.org/10.1109/dappcon.2019.00023.

    \bibitem{b8} Baldominos, A., \& Saez, Y. (2019). Coin.AI: A Proof-of-Useful-Work Scheme for Blockchain-Based Distributed Deep Learning. Entropy, 21(8), 723. https://doi.org/10.3390/e21080723.

    \bibitem{b9} Merlina, A. (2019). BlockML: A Useful Proof of Work System Based on Machine Learning Tasks. Association for Computing Machinery. https://doi.org/10.1145/3366624.3368156.

    \bibitem{b10} C. Chenli, B. Li, Y. Shi \& T. Jung. (2019). Energy-recycling Blockchain with Proof-of-Deep-Learning. IEEE International Conference on Blockchain and Cryptocurrency (ICBC), pp. 19-23. https://doi.org/10.48550/arXiv.1902.03912.

    \bibitem{b11} Lihu, A., Du, J., Barjaktarevic, I., Gerzanics, P., \& Harvilla, M. (2020). A Proof of Useful Work for Artificial Intelligence on the Blockchain. 
    https://doi.org/10.48550/arXiv.2001.09244.

    \bibitem{b12} Li, B., Chenli, C., Xu, X., Shi, Y., \& Jung, T. (2019). DLBC: A deep learning-based consensus in blockchains for deep learning services. 
    https://doi.org/10.48550/arXiv.1904.07349.

    \bibitem{b13} Lan, Y., Liu, Y., Li, B., \& Miao, C. (2021). Proof of Learning (PoLe): Empowering machine learning with consensus building on blockchains. In Proceedings of the AAAI Conference on Artificial Intelligence (Vol. 35, No. 18, pp. 16063-16066). 
    https://doi.org/10.48550/arXiv.2007.15145.

    \bibitem{b14} Chen, C., Cheng, Z., Qu, S., \& Fang, Z. (2022). Crowdsourcing Work as Mining: A Decentralized Computation and Storage Paradigm. 
    https://doi.org/10.48550/arXiv.2211.06669.
